Clinical Trial Data Analysis

### 2016-12-09 results/results.Rmd
Table of p-values from data results

print(xtable(pvalues_table_contin, 
             digits = 3,
             align = paste0(c("r|", rep("p{1in}", ncol(pvalues_table_contin))), 
                            collapse = ""),
             caption = "Comparison of p-values from four tests, for each continuous endpoint."),
      include.rownames = TRUE)
```

>>>>

summarytab <- xtable(pvalues_table_contin, 
             digits = 3,
             align = paste0(c("r|", rep("p{1.2in}", ncol(pvalues_table_contin))), 
                            collapse = ""),
             caption = "Comparison of p-values from four tests, for each continuous endpoint.")
print(summarytab, include.rownames = TRUE)

print(summarytab, include.rownames = TRUE, type="latex", file="../ms/fig/results_pvalue_summary.tex") 
```
